### 2015-05-24 docs/report/code_sharing.tex
updates report benchmarks links.

We created a benchmark to understand the difference between each approach:
\bmcode{http://jsperf.com/pjs-serialization-comparison/2}{../../spikes/2.2.1/test-syncEncodingAPI/encodingAPI.js}

@@

The benchmark with the short function was the following one:
\bmcode{http://jsperf.com/pjs-serialization/2}{../../spikes/2.2.1/test-howToSendCode/shortSerialization.js}

@@

The benchmark with the long function was the following one:
\bmcode{http://jsperf.com/pjs-serialization-long}{../../spikes/2.2.1/test-howToSendCode/longSerialization.js}

@@

The benchmark's code is the following one:
\bmcode{http://jsperf.com/pjs-encoding}{../../spikes/2.2.1/test-howToSendCodeWithData/encoding.js}

>>>>

We created a benchmark to understand the difference between each approach:
\bmcode{http://jsperf.com/pjs-serialization-comparison/4}{../../spikes/2.2.1/test-syncEncodingAPI/encodingAPI.js}

@@

The benchmark with the short function was the following one:
\bmcode{http://jsperf.com/pjs-serialization/5}{../../spikes/2.2.1/test-howToSendCode/shortSerialization.js}

@@

The benchmark with the long function was the following one:
\bmcode{http://jsperf.com/pjs-serialization-long/3}{../../spikes/2.2.1/test-howToSendCode/longSerialization.js}

@@

The benchmark's code is the following one:
\bmcode{http://jsperf.com/pjs-encoding/3}{../../spikes/2.2.1/test-howToSendCodeWithData/encoding.js}
